### 2018-04-28 Paper/cover.tex
files added

\begin{center}
\textsc{
Derivative-based global sensitivity approach to 
efficient surrogate modeling with application to molecular dynamics
}

@@

@@

Manav Vohra, Alen Alexanderian, Sankaran Mahadevan

@@

\vspace{10cm}

\begin{tabular}{ll}
Corresponding Author:  & TBA \\
                       & Vanderbilt University \\ 
                       & Nashville, TN\\ 
                       & Phone: \\ 
                       & Email: 
\end{tabular}

Submitted to: \emph{Journal of Computational Physics}

>>>>

\begin{center}
\textsc{
Derivative-based global sensitivity approach to efficient surrogate modelling
with Polynomial Chaos
}

\bigskip 
\bigskip

Manav Vohra$^{1}$, Alen Alexanderian$^{2}$, Cosmin Safta$^{3}$, Sankaran Mahadevan$^{1}$

\bigskip
\bigskip

\normalsize
$^1$Department of Civil and Environmental Engineering\\
Vanderbilt University\\
Nashville, TN 37235\\

@@

$^2$Department of Mathematics\\
North Carolina State University\\
Raleigh, NC 27695\\

@@

$^3$Sandia National Laboratories\\
Livermore, CA 94550\\

@@

\vspace{6cm}

\begin{tabbing}
Corresponding Author: \hspace{5mm} \= Sankaran Mahadevan\\
       \>  Department of Civil and Environmental Engineering\\
       \>  Vanderbilt University\\
       \>  272 Jacobs Hall, VU Mailbox: PMB 351831 \\
       \>  Nashville, TN 37235 \\
       \> \\
Phone: \> (615) 322-3040 \\
Fax:   \> (615) 343-3773 \\
Email: \>  sankaran.mahadevan@vanderbilt.edu   \\
\\
Submitted to: \> \textit{Reliability Engineering and System Safety} \\
\>  May 2018\\

\bigskip
\end{tabbing}

### 2018-04-28 Paper/intro.tex
files added

>>>>

The emerging field of uncertainty quantification (UQ) aims at methodologies for 
incorporating, characterizing, quantifying, propagating, and reducing the 
uncertainties associated with predictive models and simulations. For situations
involving complex physical models and compute-intensive simulations, an
efficient approach to construction of model surrogates is sought to enable UQ
in a tractable manner. Polynomial chaos expansion 
(PCE)~\cite{Xiu:2002,Ghanem:2003,Eldred:2008,Olivier:2010} and 
Gaussian Process (GP)~\cite{Rasmussen:2004} or Kriging~\cite{Stein:2012} are
among the most commonly used surrogates for scientific applications. However,
both approaches quickly become prohibitive when the set of uncertain model
inputs and parameters is large-dimensional. Specifically, in the case of a PCE,
a $d$-dimensional polynomial basis with a total order of truncation, $p$ 
requires model realizations at $(p+1)^d$ quadrature nodes to estimate the PC
coefficients using a fully-tensorized Gauss quadrature. This trend is 
illustrated below in Figure~\ref{fig:curse}.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.70\textwidth]{./Figures/quad_comp}
\caption{Number of fully-tensorized Gauss quadrature nodes ($(p+1)^d$) is plotted against PCE total order truncation, $p$ for $d$ = 2,3, and 4.}
\label{fig:curse}
\end{center}
\end{figure}
